Cloud Manufacturing Ecosystem - Scheduling And Evolving

### 2015-09-30 figures/user_rank.tex
two of the flow chart are done

% !TEX root = flow_head.tex
\begin{tikzpicture}[%
    >=triangle 60,              % Nice arrows; your taste may be different
    start chain=going below,    % General flow is top-to-bottom
    node distance=6mm and 60mm, % Global setup of box spacing
    every join/.style={norm},   % Default linetype for connecting boxes
    ]
% ------------------------------------------------- 
% A few box styles 
% <on chain> *and* <on grid> reduce the need for manual relative
% positioning of nodes
\tikzset{
  base/.style={draw, on chain, on grid, align=center, minimum height=4ex},
  proc/.style={base, rectangle, text width=8em},
  test/.style={base, diamond, aspect=2, text width=5em},
  term/.style={proc, rounded corners},
  % coord node style is used for placing corners of connecting lines
  coord/.style={coordinate, on chain, on grid, node distance=6mm and 25mm},
  % nmark node style is used for coordinate debugging marks
  nmark/.style={draw, cyan, circle, font={\sffamily\bfseries}},
  % -------------------------------------------------
  % Connector line styles for different parts of the diagram
  norm/.style={->, draw, lcnorm},
  free/.style={->, draw, lcfree},
  cong/.style={->, draw, lccong},
  it/.style={font={\small\itshape}}
}
% -------------------------------------------------
% Start by placing the nodes
\node [term]              (m1)  {Be Introduced};
\node [proc, join]        (p8)  {Get Initial Rank $R$};
\node [coord, yshift=2mm] (c1)  {}; \cmark{1}
\node [test, yshift=2mm]  (t1)  {Transact?};
\node [proc, yshift=-3mm] (p1)  {Increase $R$};

\node [proc, right=of t1] (p4)  {Wait};
\node [proc]              (p5)  {Compete to Get Task};
\node [test, join]        (t5)  {Make it?};
\node [coord, yshift=2mm] (c3)  {}; \cmark{3}

\node [test, yshift=2mm]  (t6)  {Outsourcing?};
\node [test]              (t7)  {Partly or Whole?};
\node [proc]              (p6)  {Submit Outsourcing Request};
\node [proc]              (p7)  {Decrease $R$};
\node [test, join]        (t8)  {$R < R_{base}$?};
\node [term]              (m2)  {Eliminate};

\node [test, left=of c3]  (t2)  {All Tasks Accomplished?};
\node [proc]              (p2)  {Process Task};
\node [test]              (t3)  {Accepted?};
\node [proc]              (p3)  {Pass the Outsouring Task};
\node [test]              (t4)  {Task Accomplished?};

\node [coord, left=of p1](c2)  {}; \cmark{2}

\draw [->, lcnorm] (p4) |- (c1);
\draw [->, lcnorm] (p8) -- (t1);
\draw [->, lcnorm] (p1) --(c2) |- (c1);

\path (t1.east)   to node [near start, yshift=1em] {$n$} (p4);
\path (t1.south) to node [near start, xshift=1em] {$y$} (p1);
  \draw [o->, lcnorm] (t1.east) -- (p4);
  \draw [*->, lcnorm] (t1.south) |- (p5);

\end{tikzpicture}

>>>>

% !TEX root = ../Eco-Model.tex
\begin{tikzpicture}[%
    >=triangle 60,              % Nice arrows; your taste may be different
    start chain=going below,    % General flow is top-to-bottom
    node distance=6mm and 60mm, % Global setup of box spacing
    every join/.style={norm},   % Default linetype for connecting boxes
    ]
% ------------------------------------------------- 
% A few box styles 
% <on chain> *and* <on grid> reduce the need for manual relative
% positioning of nodes
\tikzset{
  base/.style={draw, on chain, on grid, align=center, minimum height=4ex},
  proc/.style={base, rectangle, text width=8em},
  test/.style={base, diamond, aspect=2, text width=5em},
  term/.style={proc, rounded corners},
  % coord node style is used for placing corners of connecting lines
  coord/.style={coordinate, on chain, on grid, node distance=6mm and 25mm},
  % nmark node style is used for coordinate debugging marks
  nmark/.style={draw, cyan, circle, font={\sffamily\bfseries}},
  % -------------------------------------------------
  % Connector line styles for different parts of the diagram
  norm/.style={->, draw, lcnorm},
  free/.style={->, draw, lcfree},
  cong/.style={->, draw, lccong},
  it/.style={font={\small\itshape}}
}
% -------------------------------------------------
% Start by placing the nodes
\node [term, fill = lcfree!25]              (m1)  {Be Introduced};
\node [proc, join]        (p8)  {Get Initial Rank $R$};
\node [coord, yshift=2mm] (c1)  {}; %\cmark{1}
\node [test, yshift=2mm]  (t1)  {Transact?};
\node [proc, yshift=-2mm] (p1)  {Increase $R$};

\node [coord, yshift=0mm] (c7)  {}; %\cmark{7}

\node [test, yshift=0mm] (t2)  {All Tasks Done?};
\node [proc]              (p2)  {Process Un-Outsourceing Task};
\node [test]              (t3)  {Accepted?};
\node [proc]              (p3)  {Pass the Outsouring Task};
\node [test, join]        (t4)  {Task Done?};

\node [proc, right=of t1] (p4)  {Wait};
\node [proc]              (p5)  {Compete to Get Task};
\node [test, join]        (t5)  {Make it?};

\node [coord, yshift=2mm] (c4)  {}; %\cmark{4}

\node [test, yshift=2mm]  (t6)  {Outsourcing?};
\node [test]              (t7)  {Partly or Whole?};
\node [proc]              (p6)  {Submit Outsourcing Request};
\node [proc]              (p7)  {Decrease $R$};
\node [test, join]        (t8)  {$R < R_{base}$?};
\node [term, fill=lccong!25]              (m2)  {Eliminate};

\node [coord, left=of p1] (c2)  {}; %\cmark{2}
\node [coord, right=of t5](c3)  {}; %\cmark{3}
\node [coord, right=of p2](c5)  {}; %\cmark{5}
\node [coord, right=of t3](c6)  {}; %\cmark{6}
\node [coord, left=of c7] (c8)  {}; %\cmark{8}
\node [coord, right=of t4](c9)  {}; %\cmark{9}

\draw [->, lcnorm] (p4) |- (c1);
\draw [->, lcnorm] (p8) -- (t1);
\draw [->, lcnorm] (p1) --(c2) |- (c1);
\draw [->, lcnorm] (p2) -- (t2);
\draw [->, lcnorm] (p6) -| (c6) -- (t3);

\path (t1.east)   to node [near start, yshift=1em] {$n$} (p4);
\path (t1.south)  to node [near start, xshift=1em] {$y$} (p1);
  \draw [o->, lcnorm] (t1.east) -- (p4);
  \draw [*->, lcnorm] (t1.south) |- (p5);
\path (t2.east)   to node [near start, yshift=-1em]{$n$} ++(2mm,0);
\path (t2.north)  to node [near start, xshift=1em] {$y$} (p1);
  \draw [o->, lcnorm] (t2.east) -- (c4) ;
  \draw [*->, lcnorm] (t2.north) -- (p1);
\path (t5.east)   to node [near start, yshift=1em] {$n$} (c3);
\path (t5.south)  to node [near start, xshift=1em] {$y$} (t6);
  \draw [o->, lcnorm] (t5.east) -- (c3) |- (p4);
  \draw [*->, lcnorm] (t5.south) -- (t6);
\path (t6.west)   to node [near start, yshift=-1em]{$n$} (c5);
\path (t6.south)  to node [near start, xshift=1em] {$y$} (t7);
  \draw [*->, lcnorm] (t6.south) -- (t7);
  \draw [o->, lcnorm] (t6.west) -| (c5) -- (p2);
\path (t7.west)   to node [near start, yshift=1em] {partly} ++(-1mm,0);
\path (t7.south)  to node [near start, xshift=2em] {whole} (p6);
  \draw [*->, lcnorm] (t7.west) -| (c5);
  \draw [o->, lcnorm] (t7.south) -- (p6);
\path (t8.east)   to node [near start, yshift=1em] {$n$} ++(1mm,0);
\path (t8.south)  to node [near start, xshift=1em] {$y$} (m2);
 \draw [o->, lcnorm] (t8.east) -| (c3);
 \draw [*->, lcnorm] (t8.south) -- (m2);
\path (t3.north)  to node [near start, xshift=1em] {$n$} (p2);
\path (t3.south)  to node [near start, xshift=1em] {$y$} (p3);
  \draw [o->, lcnorm] (t3.north) -- (p2);
  \draw [*->, lcnorm] (t3.south) -- (p3);
\path (t4.west)   to node [near start, yshift=1em] {$y$} ++(-1mm,0);
\path (t4.east)   to node [near start, yshift=1em] {$n$} (c9);
  \draw [*->, lcnorm] (t4.west) -| (c8) -- (c7);
  \draw [o->, lcnorm] (t4.east) -- (c9) |- (p7);
\end{tikzpicture}
